Open OnDemand

### 2021-03-07 OOD/sections/01_intro.tex
Update to slides to point to caltech j.notebook instructions.  Merged in changes made for a class specific version to include where to contact us for support.
bring the github version up to current

\section[Why]{What can it do for me?}
\begin{frame}
	\frametitle{What can it do for me?}
	\begin{itemize}
	\item Provide a uniform environment which can help simplify instruction in a classroom setting
	\item Built-in file browser with in browser download/upload capabilities
		\begin{itemize}
		\item Max upload file size is currently limited to 5GB
		\end{itemize}
	\item In browser SSH terminal
	\item Job management and monitoring
	\item The ability to proxy graphical output from applications like Juypter notebooks and Rstudio Server executed on a compute node
	\end{itemize}
\end{frame}

>>>>

\section[Why]{What can it do for me at UH?}
\begin{frame}
	\frametitle{What can it do for me at UH?}
	\begin{itemize}
	\item Provide a uniform environment which can help simplify instruction in a classroom setting
	\item Built-in file browser with in browser download/upload capabilities
		\begin{itemize}
		\item Max upload file size is currently limited to 5GB
		\end{itemize}
	\item In browser SSH terminal
	\item Job management and monitoring
	\item The ability run interactive applications like Juypter lab/notebook, Rstudio Server and remote desktop on a node in Mana
	\end{itemize}
\end{frame}

### 2021-03-07 OOD/sections/03_custom.tex
bring the github version up to current

\subsection[rstudioenv]{Requirements \& procedure}
\begin{frame}
	\frametitle{Rstudio - Requirements \& procedure}
	\begin{block}{Requirements}
		\begin{itemize}
			\item The Lmod collection must contain a working R environment
				\begin{itemize}
					\item At a minimum it requires an R module to be loaded - lang/R
				\end{itemize}
			\item The collection must be named "rstudio"
		\end{itemize}
	\end{block}
	\begin{block}{Procedure}
		\begin{enumerate}
			\item Bring up a terminal on the cluster
			\item purge your current module environment
				\begin{itemize}
				\item module purge
				\end{itemize}
			\item Load modules you want to use with R studio
				\begin{itemize}
				\item module load lang/R/3.5.1-intel-2018.5.274-Python-2.7.15 
				\item module load data/GDAL/2.2.3-intel-2018.5.274-Python-2.7.15
				\end{itemize}
			\item Save the module environment to the name "rstudio"
				\begin{itemize}
				\item module save rstudio
				\end{itemize}
			\item Start up a new Rstudio instance and Rstudio should now have the additional libraries and be using the version of R you specified.
		\end{enumerate}
	\end{block}
\end{frame}

\section[Jupyternote]{Jupyter Notebooks}
\subsection[jupenv]{Jupyter Notebook - Custom Environment Procedure}
\begin{frame}[fragile]
	\frametitle{Jupyter Notebook - Custom Environment Procedure}
	\begin{block}{}
	The following steps were adapted from \url{https://hpc.sites.caltech.edu/documentation/software-and-modules/jupyter-notebook}.~\\The following commands should be executed from a compute node in an interactive session prior to starting up a Juypter Notebook in Open OnDemand.
	\end{block}
	\begin{semiverbatim}\footnotesize
	[\$] module load lang/Anaconda3
	[\$] conda create \ddash{}name test\_env python=3
	[\$] source activate test\_env
	\#\#\# Install your required packages \#\#\#
	\# \ldots 
	\#\#\# Finalize setup with this last package \#\#\#
	[\$(test\_env)] conda install ipykernel
	[\$(test\_env)] python -m ipykernel install \ddash{}user \ddash{}name test\_env \ddash{}display-name "test\_env"
	\#\#\# DONE and ready for use in Open OnDemand \#\#\#
 	\end{semiverbatim}
	\vspace{-1.5em}
	\begin{center}
  \includegraphics[scale=0.08]{juypter.png}
	\end{center}

@@

>>>>

\subsection[rstudioenv]{Requirements \& procedure}
\begin{frame}
	\frametitle{Rstudio - Requirements \& procedure}
	\begin{block}{Requirements}
		\begin{itemize}
			\item The Lmod collection must contain a working R environment
				\begin{itemize}
					\item At a minimum it requires an R module to be loaded - lang/R
				\end{itemize}
			\item The collection must be named "ood\_rstudio"
		\end{itemize}
	\end{block}
	\begin{block}{Procedure}
		\begin{enumerate}
			\item Bring up a terminal on the cluster
			\item purge your current module environment
				\begin{itemize}
				\item module purge
				\end{itemize}
			\item Load modules you want to use with R studio
				\begin{itemize}
				\item module load lang/R/3.5.1-intel-2018.5.274-Python-2.7.15 
				\item module load data/GDAL/2.2.3-intel-2018.5.274-Python-2.7.15
				\end{itemize}
			\item Save the module environment to the name "ood\_rstudio"
				\begin{itemize}
				\item module save ood\_rstudio
				\end{itemize}
			\item Start up a new Rstudio instance and Rstudio should now have the additional libraries and be using the version of R you specified.
		\end{enumerate}
	\end{block}
\end{frame}

\section[Jupyternote]{Jupyter Environments}
\begin{frame}[fragile]
	\frametitle{Jupyter- Custom Kernel Environment}
	\begin{block}{}
	The following steps were adapted from \url{https://hpc.sites.caltech.edu/documentation/software-and-modules/jupyter-notebook}.~\\The following commands should be executed from a compute node in an interactive session prior to starting up a Juypter Notebook in Open OnDemand.
	\end{block}
	\begin{semiverbatim}\footnotesize
	[\$] module load lang/Anaconda3
	[\$] conda create \ddash{}name test\_env python=3
	[\$] source activate test\_env
	\#\#\# Install your required packages \#\#\#
	\# \ldots 
	\#\#\# Finalize setup with this last package \#\#\#
	[\$(test\_env)] conda install ipykernel
	[\$(test\_env)] python -m ipykernel install \ddash{}user \ddash{}name test\_env \ddash{}display-name "test\_env"
	\#\#\# DONE and ready for use in Open OnDemand \#\#\#
 	\end{semiverbatim}
	\vspace{-1.5em}
	\begin{center}
  \includegraphics[scale=0.08]{juypter.png}
	\end{center}	
\end{frame}

\begin{frame}[fragile]
	\frametitle{Jupyter - Custom version}
	\begin{block}{}Users can also install a custom version of Jupyter Lab/notebook by creating a custom collection with the name "`ood\_jupyterlab"'\end{block}
	\begin{semiverbatim}\footnotesize
[\$] srun -p sandbox -c 2 --mem=6 -t 60 --pty /bin/bash
[\$] module load lang/Anaconda3
[\$] conda create -n ood_jupyterlab -c conda-forge jupyterlab=3 xeus-python
[\$] exit 
# go to OOD and create an interactive session using the existing "jupyter
notebook app/server" 
# check Jupyter notebook's about for version to verify.
 	\end{semiverbatim}

@@

\begin{frame}
  \frametitle{Jupyter Quirks}
	\begin{block}{Quirks}
			\begin{itemize}
			\item jupyter applies all parameters from a global config file and those specified at run time \url{https://jupyterlab.readthedocs.io/en/latest/user/directories.html\#labconfig-directories}.
			\item Users will need to remove or rename their global config file so as to not conflict with the Open OnDemand launcher. For example:\\ .jupyter/jupyter\_server\_config.py~->~.jupyter/jupyter\_server\_config\_custom.py
		\end{itemize}
	\end{block}
\end{frame}
